Differential Expression - MSSM-Penn-Pitt - ACC - Sex

### 2020-08-28 individual-cohorts/split_by_analysis/MSSM-Penn-Pitt_ACC_DE_Sex.Rmd
update ensembl to functional mirror and fix formula output format

# Define biomart object
mart <- biomaRt::useMart(biomart = "ENSEMBL_MART_ENSEMBL",
                host = "uswest.ensembl.org", # Ensembl Release 99 (January 2020)
                dataset = "hsapiens_gene_ensembl")

>>>>

# Define biomart object
mart <- biomaRt::useMart(biomart = "ENSEMBL_MART_ENSEMBL",
                host = "ensembl.org", # Ensembl Release 99 (January 2020)
                dataset = "hsapiens_gene_ensembl")
